Bayesian analysis of the NESTA study of interventions against verbal aggression online

### 2021-09-16 bayesianAnalysis/bayesianReport3.tex
direct effect

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/treatmentHist-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEmpiricalAdiff-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEpmiricalCdiff-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/ic-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/icc-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/correlations-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}

@@

@@

\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag2-1} \end{center}

@@

\section{Bayesian models, priors and
diagnostics}\label{bayesian-models-priors-and-diagnostics}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{comparison<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,}
\NormalTok{                     ADSITIC_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ITIC_ADSIC,}
\NormalTok{                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)}
\KeywordTok{mykable}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparison )) }
\end{Highlighting}
\end{Shaded}

@@

\begin{tabular}{lrrrrrr}
\toprule
  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
\midrule
\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.641} & \cellcolor{gray!6}{89.47387} & \cellcolor{gray!6}{0.000000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.85809} & \cellcolor{gray!6}{0.8345169}\\
tooFar & 1189.123 & 90.35400 & 4.481669 & 2.882584 & 29.76051 & 0.0887673\\
\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1189.414} & \cellcolor{gray!6}{87.19709} & \cellcolor{gray!6}{4.773490} & \cellcolor{gray!6}{5.762571} & \cellcolor{gray!6}{25.62296} & \cellcolor{gray!6}{0.0767158}\\
null & 1344.835 & 144.95033 & 160.193855 & 132.894118 & 17.16957 & 0.0000000\\
\cellcolor{gray!6}{IT} & \cellcolor{gray!6}{1345.879} & \cellcolor{gray!6}{144.64185} & \cellcolor{gray!6}{161.237934} & \cellcolor{gray!6}{132.478842} & \cellcolor{gray!6}{19.27433} & \cellcolor{gray!6}{0.0000000}\\
\addlinespace
ADSIT & 1348.714 & 142.29377 & 164.072877 & 130.485213 & 23.06652 & 0.0000000\\
\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1349.706} & \cellcolor{gray!6}{145.13624} & \cellcolor{gray!6}{165.065051} & \cellcolor{gray!6}{133.323101} & \cellcolor{gray!6}{23.10634} & \cellcolor{gray!6}{0.0000000}\\
ADSIT\_ADSIT & 1350.941 & 153.88118 & 166.300056 & 139.579270 & 32.04695 & 0.0000000\\
\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1352.972} & \cellcolor{gray!6}{154.55405} & \cellcolor{gray!6}{168.331385} & \cellcolor{gray!6}{140.054704} & \cellcolor{gray!6}{30.65579} & \cellcolor{gray!6}{0.0000000}\\
ADSITIC & 1353.603 & 147.38084 & 168.962571 & 134.581071 & 28.54365 & 0.0000000\\
\addlinespace
\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1355.210} & \cellcolor{gray!6}{148.15271} & \cellcolor{gray!6}{170.568848} & \cellcolor{gray!6}{135.609996} & \cellcolor{gray!6}{27.22326} & \cellcolor{gray!6}{0.0000000}\\
ADSITIC\_ADSIC\_ADSIT & 1355.353 & 156.53444 & 170.712149 & 142.268677 & 33.80858 & 0.0000000\\
\cellcolor{gray!6}{ADSITIC\_ADSIT\_ITIC\_ADSIC} & \cellcolor{gray!6}{1355.442} & \cellcolor{gray!6}{155.55820} & \cellcolor{gray!6}{170.800602} & \cellcolor{gray!6}{140.950680} & \cellcolor{gray!6}{34.03861} & \cellcolor{gray!6}{0.0000000}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-11-1} \end{center}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\centering
\begin{tabular}[t]{r}
\hline
x\\
\hline
0.0414089\\
\hline
0.1979211\\
\hline
0.2484756\\
\hline
-0.1097667\\
\hline
-0.0042060\\
\hline
-0.5142899\\
\hline
-0.0919148\\
\hline
-0.5302840\\
\hline
-0.0212337\\
\hline
0.1482970\\
\hline
-0.0686005\\
\hline
-0.0037630\\
\hline
-0.0117801\\
\hline
0.0118155\\
\hline
0.7945882\\
\hline
\end{tabular}
\centering
\begin{tabular}[t]{r}
\hline
x\\
\hline
0.1562753\\
\hline
0.0568494\\
\hline
0.1546028\\
\hline
0.1014546\\
\hline
0.0051643\\
\hline
0.0414267\\
\hline
0.1245614\\
\hline
0.1088835\\
\hline
0.1630179\\
\hline
0.1857528\\
\hline
0.1776783\\
\hline
0.3161707\\
\hline
0.0256771\\
\hline
0.0185521\\
\hline
0.0277774\\
\hline
\end{tabular}
\centering
\begin{tabular}[t]{r}
\hline
x\\
\hline
-0.2037740\\
\hline
0.1086423\\
\hline
0.0036955\\
\hline
-0.2678764\\
\hline
-0.0122338\\
\hline
-0.5776731\\
\hline
-0.2965873\\
\hline
-0.7023272\\
\hline
-0.2603815\\
\hline
-0.1246834\\
\hline
-0.3448157\\
\hline
-0.5084313\\
\hline
-0.0529960\\
\hline
-0.0192521\\
\hline
0.7535960\\
\hline
\end{tabular}
\centering
\begin{tabular}[t]{r}
\hline
x\\
\hline
0.2796946\\
\hline
0.2907669\\
\hline
0.4942282\\
\hline
0.0628934\\
\hline
0.0040408\\
\hline
-0.4463925\\
\hline
0.1059034\\
\hline
-0.3593766\\
\hline
0.2295494\\
\hline
0.4367149\\
\hline
0.2099344\\
\hline
0.4981378\\
\hline
0.0290304\\
\hline
0.0412303\\
\hline
0.8434971\\
\hline
\end{tabular}
\centering
\begin{tabular}[t]{r}
\hline
x\\
\hline
228.1593\\
\hline
768.4216\\
\hline
526.1494\\
\hline
418.0876\\
\hline
361.1195\\
\hline
722.3116\\
\hline
671.6673\\
\hline
823.7157\\
\hline
219.0190\\
\hline
304.7859\\
\hline
295.3412\\
\hline
829.2326\\
\hline
488.1809\\
\hline
612.3810\\
\hline
693.5845\\
\hline
\end{tabular}
\centering
\begin{tabular}[t]{r}
\hline
x\\
\hline
0.9980513\\
\hline
1.0013137\\
\hline
0.9995921\\
\hline
0.9980791\\
\hline
0.9983620\\
\hline
0.9991926\\
\hline
0.9998084\\
\hline
0.9980583\\
\hline
0.9980137\\
\hline
0.9980345\\
\hline
0.9980482\\
\hline
1.0011451\\
\hline
0.9994090\\
\hline
0.9986804\\
\hline
0.9982674\\
\hline
\end{tabular}
\end{table}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-13-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}

@@

  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
\StringTok{            }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} 
        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{, }
        \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{,}
        \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{))}\OperatorTok{+}
\StringTok{          }\KeywordTok{theme_tufte}\NormalTok{())}
\NormalTok{\}}

\NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\NormalTok{removeY,}
        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
\StringTok{        }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}

@@

  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{,}
                  \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{, }
                  \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
\NormalTok{\}}

\NormalTok{visContrastADSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}
                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{)}
                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
\StringTok{                                   }\NormalTok{removeY,}
                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}
                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}
\StringTok{                                   }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
\StringTok{                                   }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-16-1} \end{center}

>>>>

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/treatmentHist-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/violEmpiricalAdiff-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/violEpmiricalCdiff-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/ic-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/icc-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/correlations-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport3_files/figure-latex/dag1-1} \end{center}

@@

The situation is different when it comes to evaluating the \emph{direct}
effect of intervention. Then, we also need to block indirect causal
paths from the intervention to the outcome. For such an evaluation we
need to also condition on \textsf{CAS}, which is what we will do when we
turn to the study of the direct effects of the interventions.

@@

\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport3_files/figure-latex/dag2-1} \end{center}

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/priors1-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/priors03-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-6-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-7-1} \end{center}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{comparison<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,}
\NormalTok{                     ADSITIC_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ITIC_ADSIC,}
\NormalTok{                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)}
\KeywordTok{mykable}\NormalTok{(}\KeywordTok{round}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparison ),}\DecValTok{3}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

@@

\begin{tabular}{lrrrrrr}
\toprule
  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
\midrule
\cellcolor{gray!6}{tooFar} & \cellcolor{gray!6}{1185.575} & \cellcolor{gray!6}{89.393} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{27.846} & \cellcolor{gray!6}{0.487}\\
Final & 1185.657 & 89.827 & 0.082 & 2.594 & 27.614 & 0.467\\
\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1190.304} & \cellcolor{gray!6}{87.920} & \cellcolor{gray!6}{4.729} & \cellcolor{gray!6}{6.055} & \cellcolor{gray!6}{25.882} & \cellcolor{gray!6}{0.046}\\
null & 1345.358 & 145.805 & 159.783 & 134.039 & 18.061 & 0.000\\
\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1347.281} & \cellcolor{gray!6}{142.655} & \cellcolor{gray!6}{161.706} & \cellcolor{gray!6}{131.261} & \cellcolor{gray!6}{21.935} & \cellcolor{gray!6}{0.000}\\
\addlinespace
IT & 1347.916 & 146.200 & 162.341 & 134.462 & 20.545 & 0.000\\
\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1348.366} & \cellcolor{gray!6}{150.638} & \cellcolor{gray!6}{162.791} & \cellcolor{gray!6}{136.811} & \cellcolor{gray!6}{27.604} & \cellcolor{gray!6}{0.000}\\
ADSIT & 1350.067 & 144.264 & 164.492 & 132.764 & 23.985 & 0.000\\
\cellcolor{gray!6}{ADSIT\_ADSIT} & \cellcolor{gray!6}{1351.139} & \cellcolor{gray!6}{154.826} & \cellcolor{gray!6}{165.564} & \cellcolor{gray!6}{141.033} & \cellcolor{gray!6}{31.062} & \cellcolor{gray!6}{0.000}\\
ADSIC & 1351.343 & 145.539 & 165.768 & 133.454 & 25.443 & 0.000\\
\addlinespace
\cellcolor{gray!6}{ADSITIC} & \cellcolor{gray!6}{1353.020} & \cellcolor{gray!6}{147.645} & \cellcolor{gray!6}{167.445} & \cellcolor{gray!6}{135.441} & \cellcolor{gray!6}{26.884} & \cellcolor{gray!6}{0.000}\\
ADSITIC\_ADSIT\_ITIC\_ADSIC & 1355.187 & 154.826 & 169.613 & 140.659 & 34.652 & 0.000\\
\cellcolor{gray!6}{ADSITIC\_ADSIC\_ADSIT} & \cellcolor{gray!6}{1356.479} & \cellcolor{gray!6}{157.522} & \cellcolor{gray!6}{170.905} & \cellcolor{gray!6}{143.538} & \cellcolor{gray!6}{34.533} & \cellcolor{gray!6}{0.000}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-9-1} \end{center}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{mykable}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\begin{tabular}{lrrrrrr}
\toprule
  & mean & sd & X5.5. & X94.5. & n\_eff & Rhat4\\
\midrule
\cellcolor{gray!6}{a} & \cellcolor{gray!6}{0.0414089} & \cellcolor{gray!6}{0.1562753} & \cellcolor{gray!6}{-0.2037740} & \cellcolor{gray!6}{0.2796946} & \cellcolor{gray!6}{228.1593} & \cellcolor{gray!6}{0.9980513}\\
bADS[1] & 0.1979211 & 0.0568494 & 0.1086423 & 0.2907669 & 768.4216 & 1.0013137\\
\cellcolor{gray!6}{bADS[2]} & \cellcolor{gray!6}{0.2484756} & \cellcolor{gray!6}{0.1546028} & \cellcolor{gray!6}{0.0036955} & \cellcolor{gray!6}{0.4942282} & \cellcolor{gray!6}{526.1494} & \cellcolor{gray!6}{0.9995921}\\
bADS[3] & -0.1097667 & 0.1014546 & -0.2678764 & 0.0628934 & 418.0876 & 0.9980791\\
\cellcolor{gray!6}{bADSIC} & \cellcolor{gray!6}{-0.0042060} & \cellcolor{gray!6}{0.0051643} & \cellcolor{gray!6}{-0.0122338} & \cellcolor{gray!6}{0.0040408} & \cellcolor{gray!6}{361.1195} & \cellcolor{gray!6}{0.9983620}\\
\addlinespace
bCBS[1] & -0.5142899 & 0.0414267 & -0.5776731 & -0.4463925 & 722.3116 & 0.9991926\\
\cellcolor{gray!6}{bCBS[2]} & \cellcolor{gray!6}{-0.0919148} & \cellcolor{gray!6}{0.1245614} & \cellcolor{gray!6}{-0.2965873} & \cellcolor{gray!6}{0.1059034} & \cellcolor{gray!6}{671.6673} & \cellcolor{gray!6}{0.9998084}\\
bCBS[3] & -0.5302840 & 0.1088835 & -0.7023272 & -0.3593766 & 823.7157 & 0.9980583\\
\cellcolor{gray!6}{bIT[1]} & \cellcolor{gray!6}{-0.0212337} & \cellcolor{gray!6}{0.1630179} & \cellcolor{gray!6}{-0.2603815} & \cellcolor{gray!6}{0.2295494} & \cellcolor{gray!6}{219.0190} & \cellcolor{gray!6}{0.9980137}\\
bIT[2] & 0.1482970 & 0.1857528 & -0.1246834 & 0.4367149 & 304.7859 & 0.9980345\\
\addlinespace
\cellcolor{gray!6}{bIT[3]} & \cellcolor{gray!6}{-0.0686005} & \cellcolor{gray!6}{0.1776783} & \cellcolor{gray!6}{-0.3448157} & \cellcolor{gray!6}{0.2099344} & \cellcolor{gray!6}{295.3412} & \cellcolor{gray!6}{0.9980482}\\
bIC[1] & -0.0037630 & 0.3161707 & -0.5084313 & 0.4981378 & 829.2326 & 1.0011451\\
\cellcolor{gray!6}{bIC[2]} & \cellcolor{gray!6}{-0.0117801} & \cellcolor{gray!6}{0.0256771} & \cellcolor{gray!6}{-0.0529960} & \cellcolor{gray!6}{0.0290304} & \cellcolor{gray!6}{488.1809} & \cellcolor{gray!6}{0.9994090}\\
bIC[3] & 0.0118155 & 0.0185521 & -0.0192521 & 0.0412303 & 612.3810 & 0.9986804\\
\cellcolor{gray!6}{sigma} & \cellcolor{gray!6}{0.7945882} & \cellcolor{gray!6}{0.0277774} & \cellcolor{gray!6}{0.7535960} & \cellcolor{gray!6}{0.8434971} & \cellcolor{gray!6}{693.5845} & \cellcolor{gray!6}{0.9982674}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-11-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-12-1} \end{center}

@@

  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{fill =}\NormalTok{ group ))}\OperatorTok{+}
\StringTok{           }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
\StringTok{            }\KeywordTok{geom_ribbon}\NormalTok{(}\DataTypeTok{mapping =} 
        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh),  }
         \DataTypeTok{alpha =} \FloatTok{.3}\NormalTok{)}\OperatorTok{+}
\StringTok{          }\KeywordTok{theme_tufte}\NormalTok{())}
\NormalTok{\}}

\NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\NormalTok{removeY,}
        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
\StringTok{        }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-13-1} \end{center}

@@

  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{fill =}\NormalTok{ group ))}\OperatorTok{+}
\StringTok{           }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_ribbon}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }
       \DataTypeTok{alpha =} \FloatTok{.3}\NormalTok{) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
\NormalTok{\}}

\NormalTok{visContrastADSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}
                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{)}
                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
\StringTok{                                   }\NormalTok{removeY,}
                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}
                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}
\StringTok{                                   }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
\StringTok{                                   }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}

@@

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-14-1} \end{center}
